Extracting sunbeams from cucumbers: Computational reproducibility is essential for archaeological science

### 2025-02-16 README.Rmd
update zip link
update readme

1. Install [Docker](https://www.docker.com/get-started/) on your computer 
2. Download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip) and unzip    
3. Set your terminal working directory to the compendium, and run `docker build -t wos .` to build the container on your computer, it will take a few minutes and require an internet connection.
4. Run in your terminal `docker run --rm -it -e ROOT=TRUE -e PASSWORD=rstudio -dp 8787:8787 wos` to run the container
5. Go to http://localhost:8787/ with your browser and enter rstudio in both fields to start RStudio in the browser, running in the Docker container
6. In RStudio, run `rstudioapi::openProject("/home/rstudio/web-of-science-archaeology")` to open this project
7. Run `rmarkdown::render("analysis/paper/paper.qmd")` to render the Quarto document
8. When finished, to remove the Docker container and files, run this in the terminal `docker ps -aq | xargs docker stop | xargs docker rm`

>>>>

1. Install [Docker](https://www.docker.com/get-started/) on your computer 
2. Download the compendium from GitHub by clicking on the green `< > Code` button above, then click `Download ZIP`, and unzip on your computer
3. Set your terminal working directory to the compendium, and run `docker build -t wos .` to build the container on your computer, it will take a few minutes and require an internet connection.
4. Run in your terminal `docker run --rm -it -e ROOT=TRUE -e PASSWORD=rstudio -dp 8787:8787 wos` to start the container on your computer
5. Go to http://localhost:8787/ with your browser and enter `rstudio` in both fields to start RStudio in your browser, running in the Docker container with all the required depedencies installed
6. In RStudio, run `rstudioapi::openProject("/home/rstudio/web-of-science-archaeology")` to open the compendium's project
7. Run `rmarkdown::render("analysis/paper/paper.qmd")` to render the Quarto document that is the manuscript submitted for publication
8. When finished, to delete the Docker container from your computer, run this in the terminal `docker ps -aq | xargs docker stop | xargs docker rm`

### 2025-02-16 analysis/paper/paper.qmd
update readme

In Jonathon Swift's classic satirical novel *Gulliver's Travels* (1726) Gulliver visits the fictional Grand Academy of Lagado in Balnibarbi, a caricature of the Royal Society of London, and meets severals researchers working on wildly impractical projects, including one attempting to extracting sunbeams out of cucumbers.

I have presented a bibliometric analysis on the status of archaeology as a science, showing that we generally behave as social scientists If archaeological science is to continue to progress through increased consensus through the accumulation of reliable facts and methods, it is essential for researchers to take computational reproducibility seriously. Computers have become a central field and laboratory instrument for so much of our work, so we have an ethical duty to document how we change our data as it flows through silicon just as carefully as we document the operating parameters of a mass spectrometer or any other field or laboratory instrument. However, the current state of quantitative archaeology, with most researchers not using open source code, is comparable to the secrecy of alchemy prior to the emergence of chemistry. Abandoning this habit of secrecy in favour of reproducibility is vital if we are to avoid a future where our journals are filled with pretty pictures that the reader has no hope of repeating or adapting in their own work. It is time for computational reproducibility to be considered a minimum requirement for evaluating the integrity and usefulness of empirical results.

@@

>>>>

I have presented a bibliometric analysis on the status of archaeology as a science, showing distinct disunity, but that we generally behave as social scientists. If archaeological science is to continue to progress through increased consensus through the accumulation of reliable facts and methods, it is essential for researchers to take computational reproducibility seriously. Computers have become a central field and laboratory instrument for so much of our work, so we have an ethical duty to document how we change our data as it flows through silicon just as carefully as we document the operating parameters of a mass spectrometer or any other field or laboratory instrument. However, the current state of quantitative archaeology, with most researchers not using open source code, is comparable to the secrecy of alchemy prior to the emergence of chemistry. Abandoning this habit of secrecy in favour of reproducibility is vital if we are to avoid a future where our journals are filled with pretty pictures that the reader has no hope of repeating or adapting in their own work. It is time for computational reproducibility to be considered a minimum requirement for evaluating the integrity and usefulness of empirical results.

@@

In Jonathon Swift's classic satirical novel *Gulliver's Travels* (1726) Gulliver visits the fictional Grand Academy of Lagado in Balnibarbi, a caricature of the Royal Society of London, and meets several researchers working on wildly impractical projects, including one attempting to extracting sunbeams out of cucumbers.
